### 2023-11-15 calculus.tex
Fix typos
Data availability statement

  \judgment{
    \notMatchedArrow{\TMV_3} \\
    \ctxAnaTypeM{\extendCtx{\ctx}{x}{\TMV}}{\ECMV}{\TUnknown}
  }{
    \ctxAnaTypeM{\ctx}{\ECLamAnaNonMatchedArrow{x}{\TMV}{\ECMV}}{\TMV_3}
  }{MALam2}
\end{mathpar}
%
Though no expected output type is known, we still need to check and mark the body; it is thus
analyzed against the unknown type in \textsc{MKALam2}. It is possible to instead synthesize the
body, but we choose analysis so that the body is always in analytic mode. The guiding design
principle in this decision is is a notion of ``conservation of mode,'' but it is not critical to the
calculus.

@@

The semantics and metatheory presented above have been fully mechanized in the Agda proof assistant.
The mechanization additionally includes the decoupled Hazelnut action semantics described in
\cref{sec:calculus-hazelnut}.
Though the mechanization's documentation contains more detailed discussion regarding technical
decisions made therein, we highlight some important aspects here.

>>>>

  \judgment{
    \notMatchedArrow{\TMV_3} \\
    \ctxAnaTypeM{\extendCtx{\ctx}{x}{\TMV}}{\ECMV}{\TUnknown}
  }{
    \ctxAnaTypeM{\ctx}{\ECLamAnaNonMatchedArrow{x}{\TMV}{\ECMV}}{\TMV_3}
  }{MALam2}
\end{mathpar}
%
Though no expected output type is known, we still need to check and mark the body; it is thus
analyzed against the unknown type in \textsc{MKALam2}. It is possible to instead synthesize the
body, but we choose analysis so that the body is always in analytic mode. The guiding design
principle in this decision is a notion of ``conservation of mode,'' but it is not critical to the
calculus.

@@

The semantics and metatheory presented above have been fully mechanized in the Agda proof assistant.
The mechanization \cite{zhao2023} additionally includes the decoupled Hazelnut action semantics described in
\cref{sec:calculus-hazelnut}.
Though the mechanization's documentation contains more detailed discussion regarding technical
decisions made therein, we highlight some important aspects here.

### 2023-11-15 conclusion.tex
Updates from Overleaf
CCS, type classes
Data availability statement

% \section*{Acknowledgements}
% (omitted for review)

>>>>

\section*{Acknowledgements}
The authors would like to thank the anonymous referees at POPL 2024 and ICFP 2023 for helpful feedback on earlier drafts of this paper.
This work was partially funded through the NSF grant \#CCF-2238744.

\section*{Data Availability Statement}
An artifact \cite{zhao2023} containing the Agda mechanization and the implementation of Hazel
including type hole inference is available.
